### 2019-12-02 Common/chapters/deep_learning.tex
Auto stash before merge of "master" and "origin/master"
Johan and Julien: correction of little mistakes

  \begin{figure}[h!]
  \begin{center}
    \begin{tikzpicture}[
      \begin{axis}[
      	  width=0.55\linewidth, % Scale the plot to 0.7 \linewidth
          xlabel={$x$}, 
          ylabel={$y$},
          xlabel=X Axis, 
          ylabel=Y Axis,
          samples=41, 
          grid, 
          thick,
          domain=-10:10,
		legend style={at={(0,1)},anchor=north west}
        ]
        \addplot+[no marks] {func(x)};
        \addlegendentry{$ELU(x)$}
        \addplot+[no marks] {6};
        \addlegendentry{$ELU'(x)$}
      \end{axis}
    \end{tikzpicture}
    \caption{The ELU function and its derivative}
  \end{center}
\end{figure}

@@

A multilayer perceptron is an artifical neural network type. Article \cite{22} defines the multilayer perceptrons in the following way: "Multilayer perceptron are feedforward networks with one or more layers of units between the
input and output layers. The output units represent a hyperplane in the space
of the input patterns."\\
A multilayer perceptrons is composed of multiple perceptrons that are arranged into multiple layers. When the input layer receives the signal, transmits it to the hidden layer

>>>>

  \begin{figure}[h!]
  \begin{center}
    \begin{tikzpicture}[
    declare function={
    func(\x)= (\x>=0) * (x) +and (\x<0) * 4;
  }
    ]
      \begin{axis}[
      	  width=0.55\linewidth, % Scale the plot to 0.7 \linewidth
          xlabel={$x$}, 
          ylabel={$y$},
          xlabel=X Axis, 
          ylabel=Y Axis,
          samples=41, 
          grid, 
          thick,
          domain=-10:10,
		legend style={at={(0,1)},anchor=north west}
        ]
        \addplot+[no marks] {5};
        \addlegendentry{$ELU(x)$}
        \addplot+[no marks] {6};
        \addlegendentry{$ELU'(x)$}
      \end{axis}
    \end{tikzpicture}
    \caption{The ELU function and its derivative}
  \end{center}
\end{figure}

@@

A multilayer perceptron is an artifical neural network type. Article \cite{23} defines the multilayer perceptrons in the following way: "Multilayer perceptron are feedforward networks with one or more layers of units between the
input and output layers. The output units represent a hyperplane in the space
of the input patterns."\\
A multilayer perceptrons is composed of multiple perceptrons that are arranged into multiple layers. When the input layer receives the signal, transmits it to the hidden layer
